---
title: "Exploration"
author: "Sean Kent"
date: "3/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)

library(tidyverse)
library(schrute)
library(janitor)
# library(skimr)
library(lubridate)
# remotes::install_github("wilkelab/ggtext")
library(ggtext)
library(ggrepel)
```


## Pull in data

```{r}
office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')

office_ratings
```


```{r, eval = FALSE}
skimr::skim(theoffice)
```




#### Problem: datasets don't match up

- In `theoffice`, multi-part episodes (ones that aired on the same day but had the same title) are combined, but the episode number is incremented two.  
- In `office_ratings`, most of the multi-part episodes are combined, but the episode number is incremented by only 1.  This is true except in the case of season 6, which strangely splits multi-part episodes in two and thus has separate imdb ratings for each.  
- Thus, a typical join on episode number and season 


**Solution**: 

1. Take the `office_ratings` dataset and combine season 6 episodes manually 
2. create a temporary copy of `theoffice` that is summarized by season, episode, and episode name
3. make sure the two datasets line up on a row basis (even though episode numbering will be off)
4. do a manual join with `cbind`, then `left_join` the information to `theoffice` by the season-episode key


```{r}
# Niagara: Part 1 and Niagara: Part 2 are episodes 4 and 5, need to combine
niagara <- 
  office_ratings %>% 
  filter(season == 6 & episode %in% c(4,5)) %>% 
  summarize(
    season = unique(season),
    episode = min(episode),
    title = "Niagara: Parts 1 and 2",
    imdb_rating = mean(imdb_rating),
    total_votes = mean(total_votes),
    air_date = unique(air_date)
  )

# The Delivery: Part 1 and The Delivery: Part 2 are episodes 17 and 18, need to combine
thedelivery <- 
  office_ratings %>% 
  filter(season == 6 & episode %in% c(17,18)) %>% 
  summarize(
    season = unique(season),
    episode = min(episode),
    title = "The Delivery: Parts 1 and 2",
    imdb_rating = mean(imdb_rating),
    total_votes = mean(total_votes),
    air_date = unique(air_date)
  )

office_ratings2 <- 
  office_ratings %>% 
  filter(!(season == 6 & episode %in% c(4,5,17,18))) %>% 
  rbind(niagara, 
        thedelivery) %>% 
  arrange(season, episode)


```



```{r}
theoffice_episode_level <-
  theoffice %>% 
  select(season, episode, episode_name) %>% 
  unique()

theoffice_episode_level_imdb <- 
  cbind(theoffice_episode_level,
        office_ratings2 %>% select(-season, -episode, -title))

```

```{r}
theoffice_correct <-
  theoffice %>% 
  select(-imdb_rating, -total_votes, -air_date) %>% 
  left_join(
    theoffice_episode_level_imdb,
    by = c("season", "episode")
  )

saveRDS(theoffice_correct, here::here("2020/2020-03-17/theoffice-data.rds"))
```





## Visualizations

```{r}
season_begin_end_dates <- theoffice_correct %>% 
  mutate(air_date = lubridate::as_date(air_date)) %>% 
  group_by(season) %>% 
  summarize(start_date = min(air_date),
            end_date = max(air_date),
            air_date = mean(air_date),
            imdb_rating = 5)
```



```{r}
dm_grey <- rgb(182, 180, 181, maxColorValue = 255)
dm_blue <- "#3274dd"

theoffice_ep_summary <- 
  theoffice_correct %>% 
  group_by(season, episode) %>% 
  summarize(air_date = unique(air_date),
            imdb_rating = unique(imdb_rating),
            michael = "Michael" %in% character,
            director = unique(director),
            episode_name = unique(episode_name.y)
            ) %>% 
  mutate(air_date = lubridate::as_date(air_date))
```

Build the basic portions of the plot

```{r}
p <- 
  theoffice_ep_summary %>% 
  ggplot(aes(air_date, imdb_rating)) +
  geom_rect(
    aes(xmin = start_date, xmax = end_date,
        ymin = 0, ymax = 10),
    alpha = 0.3,
    fill = dm_grey,
    color = rgb(0,0,0,0),
    data = season_begin_end_dates
  ) +
  geom_point(aes(color = michael)) +
  geom_text(
    aes(label = paste0("S", as.numeric(season)), y = 0.5),
    fontface = "bold", 
    size = 5,
    data = season_begin_end_dates
  ) + 
  geom_label_repel(
    aes(label = episode_name),
    nudge_y = 1,
    size = 2.8,
    data = filter(theoffice_ep_summary, imdb_rating > 9.3, season %in% c("07", "09"))
  ) +
  scale_x_date(breaks = make_date(year = 2005:2013, month = 6, day = 1),
               date_labels = "%Y",
               # limits = c(ymd("2004-09-01"), NA)
               ) +
  scale_y_continuous(limits = c(0,10.7), breaks = 0:10, expand = c(0, 0.06)) +
  scale_color_manual(values = c(dm_blue, "black"))
```

Add some formatting and labels

```{r, fig.width=8, fig.height=5}
p <- p +
  labs(
    title = glue::glue("How <b style='color:{dm_blue}'>Michael Scott Leaving</b><i> The Office</i> Affected Fan Ratings"),
    # subtitle = "IMDB Episode Ratings over time",
    x = NULL,
    y = "IMDB Rating",
    caption = "\"Goodbye, Michael\" was the last episode with Michael Scott until \"Finale\".  Data comes from the schrutte R package and IMDB."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_markdown(lineheight = 1.1),
    legend.position = "none",
    panel.grid.major.y = element_line(color = dm_grey, linetype = "dashed"),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank()
  )

p
ggsave(here::here("2020/2020-03-17/plot_michael-scott-leaving.pdf"), width = 8, height = 5, dpi = 320)
```



## Appendix

### Diagnosing the air_date problem

```{r}
theoffice %>% 
  filter(is.na(air_date)) %>%
  # left_join(office_ratings, by = c("season", "episode")) %>% 
  select(season, episode, episode_name, air_date) %>%
  unique()
```


```{r}
theoffice %>% 
  # filter(is.na(air_date)) %>% 
  # left_join(office_ratings, by = c("season", "episode")) %>% 
  select(season, episode, episode_name, air_date, imdb_rating) %>%
  unique()

theoffice %>% 
  filter(season == "04", episode == "03") %>%
  # left_join(office_ratings, by = c("season", "episode")) %>% 
  select(season, episode, episode_name, air_date, imdb_rating) %>%
  unique()


```

```{r}
office_ratings %>% 
  select(season, episode, title, air_date) %>% 
  unique()
```

```{r}
tabyl(office_ratings, season)
tabyl(theoffice %>% select(season, episode) %>% unique(), season)
```


```{r}
office_ratings %>% filter(season == 6)
```

```{r}
theoffice %>% select(season, episode, episode_name) %>% filter(season == "06") %>% unique()
```



### Other Data Issues:

season 6 episode 24 should be "The Cover-Up", not "The cover"





